Cross-Dataset Recommender System for \\Overcoming Selection Bias

### 2022-08-24 paper/paper.tex
Prepare for experiments
Finish experiment

\subsection{Datasets}
\textbf{Imputed ML100K Dataset.}
The ML100K dataset provides 100 thousand MNAR ratings across 1683 movies rated by 944 users and is the standard large-scale dataset used for recommender systems. Since we need the ground truth ratings for controlling bias, we impute the missing ratings using standard matrix factorization.

@@

\textbf{Mixing Datasets MF.}
Pending

@@

\begin{table}
  \caption{Test set RMSE and MAE for NBPE-MF and baselines}
  \label{sample-table}
  \centering
  \begin{tabular}{lllll}
    \toprule               
            & \multicolumn{2}{c}{ML100K} & \multicolumn{2}{c}{Latent Factors}              \\
    \cmidrule(r){2-5}
            & RMSE                       & MAE                                & RMSE & MAE \\
    \midrule
    MF      & 0                          & 0                                  & 0    & 0   \\ 
    NPE-MF  & 0                          & 0                                  & 0    & 0   \\ 
    NBPE-MF & 0                          & 0                                  & 0    & 0   \\ 
    \bottomrule
  \end{tabular}
\end{table}

>>>>

\subsection{Datasets}
\textbf{Imputed ML100K Dataset.}
The ML100K dataset provides 100 thousand MNAR ratings across 1683 movies rated by 944 users and is the standard large-scale dataset used for recommender systems. Since we need the ground truth ratings for controlling bias, we impute the missing ratings using standard matrix factorization. Ratings are normalized between 0 and 1 for consistency with the other dataset.

@@

\textbf{Mixing Datasets MF.}
To analyze whether our cross-dataset model more efficiently exploits all existing data, we create a larger dataset by mixing the two differently quantized datasets and train the MF algorithm on it.

@@

\begin{table}
  \caption{Test set RMSE and MAE for NBPE-MF and baselines}
  \label{sample-table}
  \centering
  \begin{tabular}{lllll}
    \toprule               
                     & \multicolumn{2}{c}{ML100K} & \multicolumn{2}{c}{Latent Factors}                                     \\
    \cmidrule(r){2-5}
                     & RMSE                       & MAE                                & RMSE            & MAE             \\
    \midrule
    MF               & 0.1046                     & 0.0833                             & 0.1331          & 0.1045          \\ 
    NPE-MF           & 0.1048                     & 0.0834                             & 0.132           & 0.1049          \\ 
    MD-MF            & 0.1044                     & 0.083                              & 0.1299          & 0.1027          \\
    \textbf{NBPE-MF} & \textbf{0.076}             & \textbf{0.062}                     & \textbf{0.1065} & \textbf{0.0841} \\ 
    \bottomrule
  \end{tabular}
\end{table}
